```{r}

library(stringr)
library(ggplot2)
library(ggthemes)
library(delabj)
```

```{r}
protest <- read_csv(
  "~/protest.csv", na = "NULL")
```

```{r}
library(dplyr)
protest_filter <- protest %>%
  select(2, 4, 6, 15, 16, 18, 19, 23, 24)
```

```{r}
protest_sum <- aggregate(protest_filter$protest, list(protest_filter$country), sum)
colnames(protest_sum) <- c("country", "count")
```


```{r}
world_map <- map_data("world")
colnames(world_map) <- c("long", "lat", "group", "order", "country", "subregion")
```

```{r}
test <- full_join(protest_sum, world_map, by = c("country" = "country"))
test[is.na(test)] <- 0
```

#Producing World Map
```{r}
w_map <- ggplot(data = test, aes(x = long, y = lat, group = group, order = order, fill = count)) + geom_polygon(color = "white") +
  theme_delabj_dark() +
  scale_fill_viridis(option = "magma", 
                     direction = -1, name = "Number of protest", #trans="log10",
                     #limits = c(1,20000), 
                     #breaks = c(1, 100, 10000, 150000),
                     #labels = c("1", "100", "10K", "150K"),
                     guide = guide_colorbar(#order = 2,
                                            direction = "horizontal", 
                                            barheight = unit(2, units = "mm"),
                                            barwidth = unit(50, units = "mm"),
                                            draw.ulim = F, title.position = 'top', 
                                            title.hjust = 0.5, label.hjust = 0.5)) +
  labs(fill = " ",
       title = "Total <b, style = 'color:#f0435f'>protest</b> in each country since <b, style = 'color:#F19953'>1990</b>",
       caption = "") + #Sources: Harvard Dataverse \nwww.fishwongy.com
  theme(text = element_text(family = "ITC Officina Sans LT Book", size = 8),
        legend.position = "top",
        legend.key.size = unit(0.5, "cm"),
        legend.title = element_textbox(size = 10),
        legend.text=element_text(size = 12),
        axis.title = element_blank(), 
        axis.ticks = element_blank(), 
        axis.line = element_blank(), 
        axis.text = element_blank(), 
        #panel.grid = element_blank(), 
        #panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_markdown(size = 18, family="ITC Officina Sans LT Bold"),
        plot.caption = element_text(hjust = 0, family="ITC Officina Sans LT Book"))
```

#Zooming in to EU area map
```{r}
eu_map <- ggplot(data = test, aes(x = long, y = lat, group = group, order = order, fill = count)) + geom_polygon(color = "white") +
  theme_delabj_dark() + 
  coord_fixed(xlim = c(-22, 50),  ylim = c(30, 80)) +
  scale_fill_viridis(option = "magma", 
                     direction = -1, name = "Number of protest", #trans="log10",
                     #limits = c(1,20000), 
                     #breaks = c(1, 100, 10000, 150000),
                     #labels = c("1", "100", "10K", "150K"),
                     guide = guide_colorbar(#order = 2,
                                            direction = "horizontal", 
                                            barheight = unit(2, units = "mm"),
                                            barwidth = unit(50, units = "mm"),
                                            draw.ulim = F, title.position = 'top', 
                                            title.hjust = 0.5, label.hjust = 0.5)) +
  labs(fill = " ",
       title = "Total <b, style = 'color:#e85870'>protest in EU</b> since <b, style = 'color:#F19953'>1990</b>",
       caption = "") + #Sources: Harvard Dataverse \nwww.fishwongy.com
  theme(text = element_text(family = "ITC Officina Sans LT Book", size = 8),
        legend.position = "top",
        legend.key.size = unit(0.5, "cm"),
        legend.title = element_text(size = 10),
        legend.text=element_text(size = 12),
        axis.title = element_blank(), 
        axis.ticks = element_blank(), 
        axis.line = element_blank(), 
        axis.text = element_blank(), 
        #panel.grid = element_blank(), 
        #panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_markdown(size = 18, family="ITC Officina Sans LT Bold"),
        plot.caption = element_text(hjust = 0, family="ITC Officina Sans LT Book"))
```

```{r}
protest_sum_plot <- protest_sum
colnames(protest_sum_plot) <- c("country", "count")
protest_sum_plot <- filter(protest_sum_plot, count > 250)
protest_sum_plot <- protest_sum_plot[order(-protest_sum_plot$count),]
protest_sum_plot <- within(protest_sum_plot, 
                   count <- factor(count, 
                                      levels=names(sort(table(count), 
                                                        decreasing=TRUE))))
protest_sum_plot$count <- as.numeric(as.character(protest_sum_plot$count))
```

#Bar chart. Moving Y-axis within the graph instead
#Not a good idea if doing patch work
```{r}
sum_bar <- protest_sum_plot %>%
  ggplot(aes(x = reorder(country, count), y = count)) +
  #geom_hline(yintercept = c(0, 200, 400), linetype = 1, color = "grey80", size = 0.5) +
  geom_bar(stat = "identity", fill = "#83B692", width = 0.6) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right") +
  #scale_x_discrete(expand=c(0.1,0)) +
  geom_text(aes(label = count), nudge_y = -16, color = "white", 
            family="ITC Officina Sans LT Bold", size = 5) +
  annotate("text", x = c(10.5, 9.5, 8.5, 7.5, 6.5, 5.5, 4.5, 3.5, 2.5, 1.5), 
           y = c(35, 20, 20, 23, 19, 30, 30, 21, 29, 17), 
           label = c("United Kingdom", "France", "Ireland", "Germany", "Kenya", 
                     "South Korea", "Bangladesh", "Greece", "Venezuela", "China"), 
           family="ITC Officina Sans LT Book", color = "white", size = 3.5) +
  labs(y=" ", 
       x = " ", 
       title = "Who <b, style = 'color:#83B692'>marches</b> the most?",
       subtitle = "Total number of protest since <b, style = 'color:#F19953'>1990</b>",
       caption = "Sources: Harvard Dataverse\nwww.fishwongy.com") +
  theme(text = element_text(size = 8.5, family="ITC Officina Sans LT Book"),
        panel.grid.major = element_line(color = "white", size = 0.3), 
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
       axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks = element_blank(),
       axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 13),
        #axis.text.y = element_text(size = 10, family = "ITC Officina Sans LT Bold"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 24, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size = 15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 15)) +
    coord_flip() 
```

```{r}
# patchwork
w_map  / (sum_bar | eu_map) +
  ggsave("~/ProtestSum_patch.png", dpi = 320, width = 13.8, height = 12)
```






```{r}
China_protest <-
  filter(protest_filter, country == "China")
```

```{r}
China_protest2 <- aggregate(China_protest$protest, list(China_protest$location), sum)
colnames(China_protest2) <- c("city", "count")
China_protest2 <- filter(China_protest2, count > 2)
```

#Bar chart
```{r}
cn_bar <- China_protest2 %>%
  ggplot(aes(x = reorder(city, count), y = count, fill = city)) +
  #geom_hline(yintercept = c(0, 20, 40, 60), linetype = 1, color = "grey80", size = 0.5) +
  geom_bar(stat = "identity", width = 0.5) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right") +
  #scale_x_discrete(expand=c(0.13,0)) +
  geom_text(aes(label = count), nudge_y = -1.5, size = 4, color = "white", 
            family="ITC Officina Sans LT Bold") +
  scale_fill_manual("legend", values = c("Hong Kong" = "#721121", "Beijing" = "#83B692",
                                         "Chengdu" = "#83B692", "Guangzhou" = "#83B692", 
                                         "Lhasa" = "#83B692", "Liaoyang"= "#83B692", 
                                         "Shanghai" = "#83B692",  "Zhengzhou" = "#83B692")) +
 # annotate("text", x = c(8.5, 7.5, 6.5, 5.5, 4.5, 3.5, 2.5, 1.5), 
  #         y = c(4, 2.5, 3.4, 2.4, 3.3, 3.3, 4, 4), 
   #        label = c("Hong Kong", "Beijing", "Shanghai", "Lhasa", "Liaoyang", "Chengdu", 
    #                 "Guangzhou", "Zhengzhou"), color = "white", size = 3) +
  labs(y=" ", 
       x = " ", 
       title = "Who <b, style = 'color:#83B692'>marches</b> the most in China?",
       subtitle = "Total number of protest since <b, style = 'color:#F19953'>1990",
       caption = "") + #Sources: Harvard Dataverse \nwww.fishwongy.com
  
  theme(text = element_text(size = 10, family="ITC Officina Sans LT Book"),
        legend.position = "none",
       panel.grid.major = element_line(color = "white", size = 0.3), 
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 12),
        axis.text.y = element_text(size = 12, family = "ITC Officina Sans LT Bold"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 24, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size =15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 15)) +
    coord_flip() 
```



```{r}
protest_respond <- aggregate(protest_filter$protest, list(protest_filter$stateresponse1), sum)
colnames(protest_respond) <- c("respond", "count")
protest_respond <- filter(protest_respond, count > 31)
```

```{r}
protest_respond$respond[protest_respond$respond == "accomodation"] <- "Accomodation"
protest_respond$respond[protest_respond$respond == "arrests"] <- "Arrests"
protest_respond$respond[protest_respond$respond == "beatings"] <- "Beatings"
protest_respond$respond[protest_respond$respond == "crowd dispersal"] <- "Crowd dispersal"
protest_respond$respond[protest_respond$respond == "ignore"] <- "Ignore"
protest_respond$respond[protest_respond$respond == "killings"] <- "Killings"
protest_respond$respond[protest_respond$respond == "shootings"] <- "Shootings"
```



```{r}
res_bar <- protest_respond %>%
  ggplot(aes(x = reorder(respond, count), y = count, fill = respond)) +
  #geom_hline(yintercept = c(0, 2000, 4000, 6000), linetype = 1, color = "grey70", size = 0.5) +
  geom_bar(stat = "identity", width = 0.5) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right") +
  #scale_x_discrete(expand=c(0.13,0)) +
  geom_text(data = protest_respond %>% filter(count > 500),
            aes(label = count), nudge_y = -300, color = "white", 
            family="ITC Officina Sans LT Bold", size = 4) +
  scale_fill_manual("legend", values = c("Accomodation" = "#721121", "Arrests" = 
                                          "#83B692", "Beatings" = "#83B692", 
                                          "Crowd dispersal" = "#83B692", 
                                         "Ignore" = "#83B692", "Killings" = 
                                           "#83B692", "Shootings" = "#83B692")) +
  #annotate("text", x = c(7.5, 6.5, 5.5, 4.5, 3.5, 2.5, 1.5), y = c(270, 530, 290, 470, 390, 350, 300), 
   #        label = c("Ignore", "Crowd dispersal","Arrests", "Accomodation",  "Shootings", "Beatings", "Killings"), 
    #       size = 3, color = "white", family="ITC Officina Sans LT Book") +
  labs(y=" ", 
       x = " ", 
       title = "Who is in charge now",
       subtitle = "How do <b, style = 'color:#83B692'>countries respond</b> to protest?",
       caption = "") + #Sources: Harvard Dataverse\nwww.fishwongy.com
 
  theme(text = element_text(size = 8.5, family="ITC Officina Sans LT Book"),
        legend.position = "none",
        panel.grid.major = element_line(color = "white", size = 0.3), 
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 12),
        axis.text.y = element_text(size = 12, family = "ITC Officina Sans LT Bold"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 25, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size = 15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 5)) +
    coord_flip() 
```



**The dataset is not completed, some of protest only recorded how the state respond to protest but did not record the data for the number of participants. That's why the count of participant do not match the count of states' response.**
```{r}
protest_parti <- aggregate(protest_filter$protest, list(protest_filter$participants_category), sum)
colnames(protest_parti) <- c("participation", "count")
protest_parti$participation <- sub("^$", "Unknown", protest_parti$participation)
```

```{r}
protest_parti$participation <- factor(protest_parti$participation, levels = c("Unknown",">10000", "5000-10000", "2000-4999", "1000-1999", "100-999", "50-99"))
```

```{r}
parti_bar <- protest_parti %>%
  ggplot(aes(x = participation, y = count)) +
  #geom_hline(yintercept = c(-0.2, 2000, 4000), linetype = 1, color = c("black", "grey70", "grey70"), size = 0.5) +
  geom_bar(stat = "identity", fill = "#83B692", position = position_dodge(width = 0.1)) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right") +
  #scale_x_discrete(expand=c(0.15, 0)) +
  geom_text(aes(label = count), nudge_y = -200, size = 5, color = "white", family="ITC Officina Sans LT Book") +
  labs(y=" ", 
       x = " ", 
       title = "Participatation",
       subtitle = "<b, style = 'color:#83B692'>Number of participants</b> in protests",
       caption = "") + #Sources: Harvard Dataverse \nwww.fishwongy.com
  theme(text = element_text(size = 8.5, family="ITC Officina Sans LT Book"),
        panel.grid.major = element_line(color = "white", size = 0.3),
        legend.position = "none",
         panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 12),
        axis.text.y = element_text(size = 12, family = "ITC Officina Sans LT Book"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 25, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size = 15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 15)) +
    coord_flip() 
```

```{r}
protest_acco_parti <- aggregate(protest_filter$protest, list(protest_filter$stateresponse1, protest_filter$participants_category), sum)
colnames(protest_acco_parti) <- c("respond", "participation", "count")
protest_acco_parti <- filter(protest_acco_parti, respond == "accomodation")
protest_acco_parti$participation <- sub("^$", "Unknown", protest_acco_parti$participation)
protest_acco_parti$participation <- factor(protest_acco_parti$participation, levels = c("Unknown", ">10000", "5000-10000", "2000-4999", "1000-1999", "100-999", "50-99"))
```

```{r}
acco_parti_bar <- protest_acco_parti %>%
  ggplot(aes(x = participation, y = count)) +
  #geom_hline(yintercept = c(-0.2, 100, 200, 300, 400), linetype = 1, color = c("black", "grey70", "grey70", "grey70", "grey70"), size = 0.5) +
  geom_bar(stat = "identity", fill = "#83B692", position = position_dodge(width = 0.1)) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right") +
  #scale_x_discrete(expand=c(0.15, 0)) +
  geom_text(aes(label = count), nudge_y = -15, size = 5, color = "white", family="ITC Officina Sans LT Book") +
  labs(y=" ", 
       x = " ", 
       title = "Accomodation Participatation",
       subtitle = "<b, style = 'color:#83B692'>Number of participants</b> in protests that resulted in <b, style = 'color:#e85870'>accomodation",
       caption = "Sources: Harvard Dataverse \nwww.fishwongy.com") +
theme(text = element_text(size = 8.5, family="ITC Officina Sans LT Book"),
        panel.grid.major = element_line(color = "white", size = 0.3),
        legend.position = "none",
         panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 12),
        axis.text.y = element_text(size = 12, family = "ITC Officina Sans LT Book"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 25, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size = 15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 15)) +
    coord_flip() 
```


```{r}
# patchwork
res_bar  / (acco_parti_bar | parti_bar) +
  ggsave("~/PartiBar_patch.png", dpi = 320, width = 13.8, height = 12)
```


```{r}
protest_sum2 <- aggregate(protest_filter$protest, list(protest_filter$country, protest_filter$year), sum)
colnames(protest_sum2) <- c("country", "year", "count")
protest_sun2_line <-
  protest_sum2 %>%
  filter(country %in% c("United Kingdom", "China", "France", "Kenya", "South Korea", "Bangladesh"))
protest_sun2_line$country[protest_sun2_line$country == "United Kingdom"] <- "UK"
protest_sun2_line$country[protest_sun2_line$country == "South Korea"] <- "S.Korea"
protest_bar <-
  protest_sun2_line %>%
  filter(year %in% c("2010", "2015"))
```

```{r}
protest_bar$year <- as.factor(protest_bar$year)
```

```{r}
protest_bar$year <- factor(protest_bar$year, levels = c("2015", "2010"))
```

```{r}
year_bar <- protest_bar %>%
  ggplot(aes(x = reorder(country, -count), y = count, fill = year)) +
  #geom_hline(yintercept = c(-0.2, 50, 100, 150), linetype = 1, color = c("black", "grey70", "grey70", "grey70"), size = 0.5) +
  geom_bar(stat='identity', position='dodge', width = 0.7) +
  theme_delabj_dark() +
  scale_y_continuous(position = "right", limits = c(0, 160)) +
  #scale_x_discrete(expand = c(0.13,0)) +
  #scale_fill_manual(name = " ", values = c("2015" = "royalblue4", "2010" = "#76c0c1"), 
   #                 breaks = c("2010","2015")) +
  scale_fill_delabj(name = "", breaks = c("2010","2015")) +
  labs(y=" ", 
       x = " ", 
       title = "Marching era",
       subtitle = "Total number of <b, style = 'color:#83B692'>yearly protest",
       caption = "Sources: Harvard Dataverse \nwww.fishwongy.com") +
theme(text = element_text(size = 8.5, family="ITC Officina Sans LT Book"),
        panel.grid.major = element_line(color = "white", size = 0.3),
        legend.position = c(-0.03, 1.06),
        legend.direction = "horizontal",
        legend.key.size = unit(0.3, "cm"),
        legend.text=element_text(size = 12),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x.top = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(family = "ITC Officina Sans LT Bold", size = 12),
        axis.text.y = element_text(size = 12, family = "ITC Officina Sans LT Bold"),
        plot.title = element_markdown(hjust = 0, vjust=-0.12, size = 24, 
                                  family="ITC Officina Sans LT Bold"),
        plot.subtitle = element_markdown(hjust = 0, vjust=-1.5, size = 15),
       plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0, vjust = -2.5, size = 15)) +
  coord_flip() 
```

```{r}
# patchwork
cn_bar  / year_bar +
  ggsave("~/BarChart_patch.png", dpi = 320, width = 13.8, height = 12)
```
